---
title: "mhealthtools"
author: "Meghasyam Tummalacherla"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mhealthtools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Purpose

The current Vignette is something of a metaVignette list as in the sense it gives a list of entities that need Vignettes for the mhealthtools package

## List of required Vignettes
1. Introduction:    
    1.1 Installation of the package     
    1.2 Loading the data     
    1.3 Tasks / activities the package is applicable to     

2. Functionality:    
  2.1 Structure of package (Using in built model vs specifying a model)    
  2.2 List of functions    

3. Applicability of Package:    
  3.1 Tremor tasks    
  3.2 Tapping tasks    
  3.3 Voice tasks    
  3.4 Specifying your own model    

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
